A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-04 ionic_liquids.tex
some comments on conclusions

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].

@@

In Fig.~\ref{fig:pressure} we present for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably smaller for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).

@@

On of the goals of this study was to compare available force fields for \ce{[emim][B(CN)_4]}.
The model that best reproduces the experimental density is the one developed by Koller.
This is the only model that reparametrizes the LJ parameters for the boron atom.
We demonstrate that it is possible to employ rigid bodies and the DSF method for the simulation. 
computationally more efficient.
Using the expanded ensemble method, we reproduced the solvation free energy.
Koller best reproduces the experimental henry constants. 
This model was evaluated also to predict inifinite-dilution activity coefficient.
This property also depends in the solvation free energy of the pure solutes.
The results at infinite-dilution suggest a more favorable solvation. and high concentrations 
The pictures changes

>>>>

Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
The differences in \ce{CO_2} molar fractions for this ILs exemplifies the observations made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.

@@

In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably smaller for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).

@@

One of the goals of this paper was to compare available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
We have found that only the model of Koller \textit{et al.} \cite{Koller_2012} achieves this goal.
A key factor for this success seems to be the reparametrization of the LJ parameters for the boron atom, which is only performed in the work of Koller \textit{et al.}  \cite{Koller_2012} in order to reproduce the experimental density of the pure substance.

In the case of \ce{[emim][B(CN)_4]}, we were able to

to introduce computationally efficient strategies, such as the use of rigid bodies and the DSF method for evaluating the Co the simulations and perform them in a more computationally efficient way: the ILs were modelled as rigid bodies and using the DSF method to calculate the Coulombic interactions.
This required some preliminary simulations in order to analyze the most probable conformations of the ions.
This was carried out in a simple way and with very good results.

Using the expanded ensemble method, we reproduced the solvation free energy for both systems of interest:
\ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} and at different thermodyanamic conditions. 
At infinite-dilution those solvents performs in the solvation in \ce{[emim][B(CN)_4]} only slightly more favorable.
This picture completely changed when we analyzed the systems at higher concentrations: the pressure required to dissolved a certain mass of \ce{CO_2} is considerable smaller that for \ce{[emim][NTf_2]}.

This model was evaluated also to predict inifinite-dilution activity coefficient.
This property also depends in the solvation free energy of the pure solutes.
